---
title: "Data Analytics Project"
description: |
  Elea Bornand & Roman Alt
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r results="asis"}
cat(readLines('text/home.txt'), sep = '\n')
```

# 4 Results
Currently, we can display the development of the average happiness score as well as a baseline graph before the 24.2.2022 (i.e., first day of invasion) for <i>German</i> Twitter users.
Also, we've got the processed Hedonometer data as well as the variables <i>Language, Capital and Iso2 code</i> for all relevant countries.

```{r echo=FALSE, eval=FALSE}
install.packages("rjson")
install.packages("ggplot2")
install.packages("lemon")
library("rjson")
library("lemon")
knit_print.data.frame <- lemon_print
source("code/JSON_handler.R")
source("code/plotter.R")

de_habit_json <- fromJSON(file = "http://hedonometer.org/api/v1/happiness/?format=json&timeseries__title=de_all&date__gte=2022-02-24&limit=1000")
de_base_json <- fromJSON(file = "http://hedonometer.org/api/v1/happiness/?format=json&timeseries__title=de_all&date__gte=2022-01-24&limit=31")

data_de_habit <- function.createHedonDataFrame(de_habit_json)
data_de_base <- function.createHedonDataFrame(de_base_json)


#creating a plot for the german language
plot_de_habit <- function.basic_plot(data_de_habit)
plot_de_base <- function.basic_plot(data_de_base)
```
#### Hedonometer Data
```{r render=lemon_print}
hedonometer_data

```
#### Countries Data
```{r render=lemon_print}
head(countries_capitals_and_more, 6)

```

### Development of Happiness (average happiness score) since 24.2.2022 for German Twitter users:

```{r}
final_plot

```


# 5 Limitations
[Work in progress.]

### More information
<ul>
<li>On the Hedonometer in general: https://hedonometer.org/timeseries/en_all/?from=2020-10-06&to=2022-04-05</li>
<li>On the wordlists used for the Hedonometer (e.g., English): https://hedonometer.org/words/labMT-en-v2/</li>
<li>On the Hedonometer data: https://hedonometer.org/api.html</li>
</ul>
 
### References
<ul>
<li>Alfarsi, H. (2022). https://www.profolus.com/topics/causes-of-the-russia-ukraine-conflict-an-explainer/ [04.01.2022]</li>
<li>Dan, V., & Brosius, H. B. (2021). The onset of habituation effects: Predicting fluctuations in news use during the COVID-19 pandemic by disease occurrence. European Journal of Health Communication, 2(3), 44-61. https://doi.org/10.47368/ejhc.2021.303</li>
<li>Dodds, P. S., Harris, K. D., Kloumann, I. M., Bliss, C. A., & Danforth, C. M. (2011). Temporal patterns of happiness and information in a global social network: Hedonometrics and Twitter. PloS one, 6(12), e26752. https://doi.org/10.1371/journal.pone.0026752</li>
<li>Dodds, P. S., & Danforth, C. M. (2010). Measuring the happiness of large-scale written expression: Songs, blogs, and presidents. Journal of happiness studies, 11(4), 441-456. https://doi.org/10.1007/s10902-009-9150-9</li>
<li>Global Conflict Tracker (2022). https://www.cfr.org/global-conflict-tracker/conflict/conflict-ukraine [04.01.2022]</li>
<li>Infoplease (2022). https://www.infoplease.com/world/countries/languages-spoken-in-each-country-of-the-world [04.01.2022]</li>
<li>Johnson, B., & Alluri, A. (2022). If you’re happy and you know it, write a tweet. http://www.marketplace.org/2015/02/10/tech/if-youre-happy-and-you-know-it-write-tweet [04.01.2022]</li>
<li>Qiao, F., & Jiang, K. (2021). Attitudes Towards Global Warming on Twitter: A Hedonometer-Appraisal Analysis. Journal of Global Information Management (JGIM), 30(7), 1-20. https://doi.org/10.4018/JGIM.296708</li>
</ul>