---
title: "Data Analytics Project"
description: |
  Elea Bornand & Roman Alt
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r results="asis"}
cat(readLines('text/home.txt'), sep = '\n')
```

# Results
At the moment, we can show the development of the average happiness score as well as a baseline graph before the 24.2.2022 (i.e., first day of invasion) for <i>German</i> Twitter users.
Also, we've got the processed data from hedonometer.org as well as the variables <i>Language, Capital and Iso2 code</i> for all relevant countries.

```{r echo=FALSE, eval=FALSE}
install.packages("rjson")
install.packages("ggplot2")
install.packages("lemon")
library("rjson")
library("lemon")
knit_print.data.frame <- lemon_print
source("code/JSON_handler.R")
source("code/plotter.R")

de_habit_json <- fromJSON(file = "http://hedonometer.org/api/v1/happiness/?format=json&timeseries__title=de_all&date__gte=2022-02-24&limit=1000")
de_base_json <- fromJSON(file = "http://hedonometer.org/api/v1/happiness/?format=json&timeseries__title=de_all&date__gte=2022-01-24&limit=31")

data_de_habit <- function.createHedonDataFrame(de_habit_json)
data_de_base <- function.createHedonDataFrame(de_base_json)


#creating a plot for the german language
plot_de_habit <- function.basic_plot(data_de_habit)
plot_de_base <- function.basic_plot(data_de_base)
```
#### Hedonometer Data
```{r render=lemon_print}
hedonometer_data

```
#### Countries Data
```{r render=lemon_print}
head(countries_capitals_and_more, 6)

```

### Development of Happiness (average happiness score) since 24.2.2022 for German Twitter users:

```{r}
plot_de_habit

```
### Baseline of Happiness (average happiness score) starting 1 month before 24.2.2022 for German Twitter users:

```{r}
plot_de_base

